Data analysis

### 2025-04-04 processing/02-analysis.qmd
Up analysis

m2 <- lmer(mjp ~ 1 + ola_num + ola_2 + (1 | idencuesta),
                data = df_study1)

m3 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + (1 | idencuesta), data = df_study1)

m4 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + (1 | idencuesta),
                data = df_study1)

m5 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort + (1 | idencuesta),
                data = df_study1)

m6 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort + merit_talent + (1 | idencuesta),
                data = df_study1)

m7 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + (1 | idencuesta),
                data = df_study1)

m8 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 | idencuesta),
                data = df_study1)

@@

>>>>

m1.1 <- lmer(mjp ~ 1 + ola_num + ola_2 + (1 | idencuesta),
                data = df_study1)

m2 <- lmer(mjp ~ 1 + ola_num + ola_2 + (1 + ola_num | idencuesta),
                data = df_study1)

anova(m1.1, m2)

m3 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + (1 + ola_num | idencuesta), 
           data = df_study1)

m4 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + (1 + ola_num | idencuesta),
                data = df_study1)

m5 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort + (1 + ola_num | idencuesta),
                data = df_study1)

m6 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort + merit_talent + (1 + ola_num | idencuesta),
                data = df_study1)

m7 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + (1 + ola_num | idencuesta),
                data = df_study1)

m8 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + ola_num | idencuesta),
                data = df_study1)

m9 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality*ola_num + just_inequality + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + ola_num | idencuesta),
                data = df_study1)

m10 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality*ola_num + just_inequality*ola_num + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + ola_num | idencuesta),
                data = df_study1)

m11 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality*ola_num + just_inequality*ola_num + merit_effort*ola_num + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + ola_num | idencuesta),
                data = df_study1)

m12 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality*ola_num + just_inequality*ola_num + merit_effort*ola_num + merit_talent*ola_num + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + ola_num | idencuesta),
                data = df_study1)
```

@@

```{r}
#| label: tbl-interactions
#| results: asis
#| tbl-cap: "Time interactions within effects for market justice preferences"
#| tbl-cap-location: top

ccoef <- list(
  "(Intercept)" = "Intercept",
  "ola_num:perc_inequality" = "Perception inequality (WE) x Wave",
  "ola_num:just_inequality" = "Justification inequality (WE) x Wave",
  "ola_num:merit_effort" = "Merit: Effort (WE) x Wave",
  "ola_num:merit_talent" = "Merit: Talent (WE) x Wave"
  )

texreg::htmlreg(list(m9,m10,m11,m12),
               custom.model.names = c(paste0("Model ", seq(9:12))),
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 3,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. %stars.",
               threeparttable = T,
               leading.zero = T,
               float.pos = "h!",
               use.packages = F,
               booktabs = T,
               scalebox = 1)
```
